Informing policy via dynamic models: Cholera in Haiti

### 2024-01-24 ms.Rnw
Fixed broken file path

# Load the file containing profiles of Model 1 Parameters.
if (RUN_LEVEL != 3 && file.exists("model1/run_level_3/h1_profiles.rds")) {
  h1_prof <- readRDS("model1/run_level_3/h1_profiles.rds")
} else if (file.exists(paste0('model1', rl_dir, 'h1_profiles.rds'))) {
  h1_prof <- readRDS(paste0('model1', rl_dir, 'h1_profiles.rds'))
} else {
  stop(paste0("Missing file: `model1/", rl_dir, 'h1_profiles.rds`;\nThe file can be obtained by running the script `H1profile.R`'))
}

@@

  # If RUN_LEVEL != 3, and RUN_LEVEL == 3 results exist, just load the RL3
  # results.
  h3_prof <- readRDS("model3/run_level_3/h3_profiles.rds")
} else if (file.exists(paste0('model3', rl_dir, 'h3_profiles.rds'))) {

  # If the `model3/run_level_<RUN_LEVEL>/h3_profiles.rds` file exists, load it
  h3_prof <- readRDS(paste0('model3', rl_dir, 'h3_profiles.rds'))
} else {

>>>>

# Load the file containing profiles of Model 1 Parameters.
if (RUN_LEVEL != 3 && file.exists("model1/run_level_3/h1_profiles.rds")) {
  h1_prof <- readRDS("model1/run_level_3/h1_profiles.rds")
} else if (file.exists(paste0('model1/', rl_dir, 'h1_profiles.rds'))) {
  h1_prof <- readRDS(paste0('model1/', rl_dir, 'h1_profiles.rds'))
} else {
  stop(paste0("Missing file: `model1/", rl_dir, 'h1_profiles.rds`;\nThe file can be obtained by running the script `H1profile.R`'))
}

@@

  # If RUN_LEVEL != 3, and RUN_LEVEL == 3 results exist, just load the RL3
  # results.
  h3_prof <- readRDS("model3/run_level_3/h3_profiles.rds")
} else if (file.exists(paste0('model3/', rl_dir, 'h3_profiles.rds'))) {

  # If the `model3/run_level_<RUN_LEVEL>/h3_profiles.rds` file exists, load it
  h3_prof <- readRDS(paste0('model3/', rl_dir, 'h3_profiles.rds'))
} else {
